Verifying Demonstrations

### 2018-05-23 paper/DB-anon-cred.tex
Edits distance bounding and DB-anon-cred

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge, instead of \ac{DBPK}.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie for 
proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need 
\iac{DBPK} protocol for discrete logarithms.
To realize this, we will now introduce such a protocol that will allow us to do 
\ac{DB} anonymous credentials.
We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
\ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.

\NewCryptoScheme{\DBS}{DBS}
\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
\NewAlgorithm{\DBSverify}{\DBS.\!Verify}

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and an impersonating 
verifier (\ie public-key).
It will not protect against terrorist fraud, although ideally this property should be desirable.

@@

The protocol is also secure against distance hijacking due to the fact that it is the authenticating bit string that is used 
during the \ac{DB} phase.

>>>>

There is a protocol which provide \ac{DBPK} with all the desired properties from 
above, ProProx~\cite{ProProx}.
(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
Knowledge, instead of \ac{DBPK}.)
However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie 
protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we 
need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = 
  g^\alpha]\)).
To realize this, we will now introduce such a protocol that will allow us to do 
\ac{DB} anonymous credentials.

\NewScheme{\DBS}{DBS}
\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
\NewAlgorithm{\DBSverify}{\DBS.\!Verify}

\emph{Reattempting \iacl{DB} Schnorr protocol.}
In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
design a distance-bounding protocol based on the Schnorr identification 
scheme~\cite{Schnorr}.
That \ac{DB} Schnorr protocol was shown to be prone to distance 
hijacking~\cite{DistanceHijacking}.
(It could not fulfil \ac{DBTF} either.)
We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
impersonating verifier (\ie it is public-key).

@@

The protocol is \ac{DBTF} resistant, if the malicious prover gives both 
responses to the adversary, the adversary can compute the secret key.
This follows from the fact that it is \iac{ZKPK}, \ie there is an extractor that 
can extract the secret.

The protocol is also secure against distance hijacking due to the fact that it 
is the authenticating bit string that is used during the \ac{DB} phase, not the 
challenge bit string as in Brands-Chaum.

### 2018-05-23 paper/DistanceBounding.tex
Edits distance bounding and DB-anon-cred

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks contactless communications in which the adversary forwards a communication between a prover and a possibility far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic tools as they are independent of the semantics of the messages exchanged and mechanisms ensuring the physical proximity between a verifier and a prover must be used.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
    far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
\daniel{Describe the DB frauds in more detail, i.e. explain them.}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).

>>>>

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent 
relay attacks in contactless communications in which the adversary forwards a 
communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic tools as they are independent 
of the semantics of the messages exchanged, so mechanisms ensuring the physical 
proximity between a verifier and a prover must be used.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account.
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.

The main security requirements of \ac{DB} protocols can be summarized as follows:
\begin{itemize}
  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
    far-away honest prover.
  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
\end{itemize}
\daniel{Describe the DB frauds in more detail, \ie explain them.}
There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier 
as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials 
(which we do in \cref{DB-anon-cred}).
The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
